### 2021-06-06 paper/report.tex
channel replaces intervention in shapley plot.

        The decomposition is based on Shapley values where the individual contribution of an intervention is its average contribution over different sizes of coalitions (combinations with other interventions). The individual contribution to a coalition is the difference between the effect size of the coalition with the particular intervention and without.
    }
\end{figure}

>>>>

        The decomposition is based on Shapley values where the individual contribution of a channel is its average contribution over different sizes of coalitions (combinations with other channels). The individual contribution to a coalition is the difference between the effect size of the coalition with the particular channel and without.
    }
\end{figure}
